\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-03-04 paper/subdocuments/results.Rnw
fixed plot with "zero-gini"

<<setup>>=
library(foreign)
library(ggplot2)
df <- read.dta("../../data/ginis_und_perzentile.dta")
df$zeros <- df$null_norm/df$cpop # i only use normal cases here
@

>>>>

<<setup>>=
library(foreign)
library(ggplot2)
df <- read.dta("data/ginis_und_perzentile.dta")
df$zeros <- df$null_norm/df$cpop # i only use normal cases here
@
